---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# phsverse

This package is created with [metamakr](https://github.com/jdtrat/metamakr) and
combines three of our [Public Health Scotland (PHS)](https://www.publichealthscotland.scot/) packages on GitHub:

- [phstemplates](https://github.com/Public-Health-Scotland/phstemplates)
- [phsmethods](https://github.com/Public-Health-Scotland/phsmethods)
- [phsstyles](https://github.com/Public-Health-Scotland/phsstyles)

## Installation

To install `phsverse`, the package `remotes` is required, and can be installed with `install.packages("remotes")`.

You can then install `phsverse` on RStudio server from GitHub with:

```{r gh-installation, eval = FALSE}
remotes::install_github("Public-Health-Scotland/phsverse",
  upgrade = "never"
)
```

Network security settings may prevent `remotes::install_github()` from working on RStudio desktop. If this is the case, `phsverse` can be installed by downloading the [zip of the repository](https://github.com/Public-Health-Scotland/phsverse/archive/master.zip) and running the following code (replacing the section marked `<>`, including the arrows themselves):

```{r source-installation, eval = FALSE}
remotes::install_local("<FILEPATH OF ZIPPED FILE>/phsverse-master.zip",
  upgrade = "never"
)
```

## Using phsverse

Load `phsverse` using `library()`:

```{r load}
library(phsverse)
```
